quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2024-06-22 paper-quollr.Rmd
Add indicating line segments section

@@

@@

>>>>

<!--add each step separately-->

@@

```{r, echo=TRUE, eval=FALSE}
find_low_dens_hex(
  df_bin_centroids_all = df_bin_centroids, 
  bin1 = 12, 
  df_bin_centroids_low = df_bin_centroids_low
  )

@@

To indicate neighbors, the `tri_bin_centroids()` function is used to triangulate bin centroids. Following this, `gen_edges()` function computes the line segments that connect neighboring bins by providing the triangulated data. This results the coordinates that generate the connecting lines.
